Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-12-06 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

\newpage
### Introduction
**See comment 4,31**
Forests globally play a critical role in climate regulation [@bonan_forests_2008], yet there remains enormous uncertainty as to how the terrestrial carbon (C) sink, which is dominated by forests, will respond to climate change [@friedlingstein_climatecarbon_2006]. An important aspect of this uncertainty lies with physiological responses of trees to drought [@kennedy_implementing_2019]. In many forested regions around the world, the risk of severe drought is increasing [@trenberth_global_2014; @cook_global_2014; @cook_unprecedented_2015; @mankin_mid-latitude_2019], sometimes despite increasing precipitation [@intergovernmental_panel_on_climate_change_climate_2015]. Droughts, exasperated by climate change, have been affecting forests worldwide [@allen_global_2010], and are expected to continue severely impacting forests [@anderegg_consequences_2013; @adams_temperature_2009; @breda_temperate_2006; @hartmann_research_2018; @allen_underestimation_2015; @abrams_interdisciplinary_2016; @adams_multi-species_2017]**too many refs here. reduce to 2-3**. However, the traits that predict tree growth and mortality responses to drought have been under debate, and are difficult to resolve with the limited available census data, which only rarely includes extreme drought. The aim of this study was to test how tree size and traits shaped growth responses to historical droughts in the tree-ring record.

>>>>

\newpage
### Introduction
**See comment 4,31**
Forests globally play a critical role in climate regulation [@bonan_forests_2008], yet there remains enormous uncertainty as to how the terrestrial carbon (C) sink, which is dominated by forests, will respond to climate change [@friedlingstein_climatecarbon_2006]. An important aspect of this uncertainty lies with physiological responses of trees to drought [@kennedy_implementing_2019]. In many forested regions around the world, the risk of severe drought is increasing [@trenberth_global_2014; @cook_global_2014; @cook_unprecedented_2015; @mankin_mid-latitude_2019], sometimes despite increasing precipitation [@intergovernmental_panel_on_climate_change_climate_2015]. Droughts, exasperated by climate change, have been affecting forests worldwide [@allen_global_2010], and are expected to continue severely impacting forests [@anderegg_consequences_2013; @adams_temperature_2009; @breda_temperate_2006; @hartmann_research_2018; @allen_underestimation_2015; @abrams_interdisciplinary_2016; @adams_multi-species_2017]**too many refs here. reduce to 2-3**. However, it is difficult to resolve factors conferring drought resistance in trees with the limited available census data, which only rarely includes extreme drought. The aim of this study was to test how tree size and traits shaped growth responses to historical droughts in the tree-ring record.
